\documentclass[a4paper,11pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[top=1cm, bottom=1cm, left=1.2cm, right=1.2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}

% --- COLORS ---
\definecolor{darkgrey}{RGB}{40,40,40}
\definecolor{accent}{RGB}{204, 36, 29} % Gruvbox Red

% --- CONFIGURATION ---
\hypersetup{colorlinks=true, linkcolor=accent, urlcolor=accent}
\setlength{\parindent}{0pt}

\titlespacing*{\section}{0pt}{8pt}{4pt}
\titleformat{\section}{\large\bfseries\color{darkgrey}\uppercase}{}{0em}{}[\titlerule]

% --- CUSTOM COMMANDS ---
\newcommand{\entry}[4]{
  \vspace{2pt}
  {\bfseries #1} \textbullet\ \textit{#2} \hfill \textbf{\footnotesize #3} \\
  {\small #4} \par 
  \vspace{4pt}
}

\newcommand{\project}[3]{
  \vspace{2pt}
  {\bfseries #1} \hfill \textit{\footnotesize #2} \\
  {\small #3} \par
  \vspace{3pt}
}

\newcommand{\award}[3]{
  \vspace{2pt}
  {\bfseries #1} \hfill \textbf{\footnotesize #2} \\
  {\small #3} \par
  \vspace{2pt}
}

% --- DOCUMENT ---
\begin{document}
\pagestyle{empty}

% --- HEADER ---
\begin{center}
    {\LARGE \textbf{Mario Enrique Ramírez Gallardo}} \\ \vspace{2pt}
    {\large Software Engineer | Product Builder} \\ \vspace{4pt} \\ \vspace{4pt}
    
    \small
    \faEnvelope\ \href{mailto:ragm030119@gs.utm.mx}{ragm030119@gs.utm.mx} \quad \textbullet \quad
    \faPhone\ (+52) 951 119 6182 \quad \textbullet \quad
    \faGithub\ \href{https://github.com/p3p3p3k4z}{p3p3p3k4z} \quad \textbullet \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/mario-ramirez-abab9a318/}{/in/mario-ramirez} \\
    \faGlobe\ \href{https://marioramirez-dev.vercel.app/}{marioramirez-dev.vercel.app}
\end{center}

\vspace{-6pt}

% --- ABOUT ME ---
\section*{About Me}
\small Software Engineer with a solid background in Computer Engineering and proficiency in Linux environments. Specializing in the architecture and development of scalable Web and Mobile applications. I have hands-on experience in systems development and the creation of modular components. I excel in my analytical ability to solve complex problems under pressure, focusing on delivering scalable, maintainable code and results-oriented solutions.

% --- EXPERIENCE ---
\section*{Professional Experience}

\entry{Teteocan Technologies}{Software Developer Intern}{Apr 2025 -- Sept 2025}
{Architected cross-platform mobile solutions using \textbf{Flutter} and \textbf{Dart}, building modular components that accelerated the development cycle. Designed the \textbf{Firebase} infrastructure with real-time synchronization, structuring security rules and optimizing the database schema to significantly reduce latency in critical queries, ensuring app scalability.}

% --- PROJECTS ---
\section*{Featured Projects}

\project{\href{https://github.com/p3p3p3k4z/aniita-web}{Añi Ita (Soul of the Flower) \faGithub}}{Python, Web, NASA Data}{
Environmental restoration engine using \textbf{Landsat/MODIS} satellite data to automate the design of "Pollinator Islands". Features predictive flora models and an immersive 3D "Bee Mode" for visual validation.}

\project{\href{https://github.com/p3p3p3k4z/huellazo-solana}{Huellazo (Solana LATAM Hackathon) \faGithub}}{React, Solana, Rust, NFTs}{
Sustainable tourism platform gamifying ecological impact via blockchain. Developed integration using custom RPCs, earning a **direct pass to the incubation phase**.}

\project{\href{https://github.com/p3p3p3k4z/Haskell-ML-Cat}{Haskell ML Cat \faGithub}}{Haskell, Python, Hasktorch, IPC}{
High-performance benchmarking system. Hybrid architecture connecting a functional Haskell backend with a Python interface via \textbf{IPC}, comparing KNN models against Deep Learning.}

% --- ACHIEVEMENTS ---
\section*{Achievements and Awards}

\award{3rd Place -- CLIHC (Latin American Conf. on Human-Computer Interaction)}{2026}{
International recognition for innovation in user-centered interface design and development with social impact.}

\award{Top 20 Finalist -- HackODS UNAM}{2026}{
Development of technological solutions and data visualization using open data portals (INEGI, UNAM) for the SDGs.}

\award{Global Top 5 -- Bolt x MiniMax VIBE HACKERS}{2025}{
Solo development of "Polli Vision", an AI vision tool for real-time species identification in under 48h.}

\award{Local Winner (4th Place) -- NASA Space Apps Challenge}{2024}{
Development of "Cozobi", an agricultural optimization solution based on geospatial telemetry.}

% --- SKILLS ---
\section*{Skills}
\small
\textbf{Languages:} Python, JavaScript/TypeScript, Dart, SQL, C, Bash. \\
\textbf{Infrastructure \& Systems:} Linux, Docker, Git, CI/CD. \\
\textbf{Web \& Mobile:} React, Next.js, Vite, Tailwind CSS, Flutter. \\
\textbf{Interests:} DevOps, Machine Learning, Web3, Systems Development.

% --- EDUCATION AND CERTIFICATIONS ---
\section*{Education and Certifications}

\textbf{B.S. in Computer Engineering (Expected 2026)} \hfill \textit{Universidad Tecnológica de la Mixteca} \par \vspace{4pt}

\textbf{Machine Learning Engineer \& Associate Python Developer} \hfill \textit{DataCamp} \par \vspace{4pt}

\textbf{Professional DevOps Path} \hfill \textit{CódigoFacilito} \par \vspace{4pt}

\textbf{Back-end Specialization} \hfill \textit{Oracle Next Education (ONE) G7} \par \vspace{4pt}

\textbf{OCI Foundations Associate 2025} \hfill \textit{Oracle} \par

\end{document}